% Created 2018-06-25 Mo 13:07
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{scrreprt}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{units}
\usepackage{siunitx}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage[authoryear,round]{natbib}
\title{GPROF-NN: A neural network based implementation of the Goddard Profiling Algorithm}
\subtitle{Response to reviewer comments}
\date{}
\hypersetup{
 pdfauthor={Simon Pfreundschuh},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 24.5.1}, 
 pdflang={English}}

\RequirePackage[normalem]{ulem} %DIF PREAMBLE
\RequirePackage{luacolor}\definecolor{RED}{rgb}{1,0,0}\definecolor{BLUE}{rgb}{0,0,1} %DIF PREAMBLE
\providecommand{\DIFadd}[1]{{\protect\textcolor{blue}{\uwave{#1}}}} %DIF PREAMBLE
\providecommand{\DIFdel}[1]{{\protect\textcolor{red}{\sout{#1}}}}                      %DIF PREAMBLE
%DIF SAFE PREAMBLE %DIF PREAMBLE
\providecommand{\DIFaddbegin}{} %DIF PREAMBLE
\providecommand{\DIFaddend}{} %DIF PREAMBLE
\providecommand{\DIFdelbegin}{} %DIF PREAMBLE
\providecommand{\DIFdelend}{} %DIF PREAMBLE
%DIF FLOATSAFE PREAMBLE %DIF PREAMBLE
\providecommand{\DIFaddFL}[1]{\DIFadd{#1}} %DIF PREAMBLE
\providecommand{\DIFdelFL}[1]{\DIFdel{#1}} %DIF PREAMBLE
\providecommand{\DIFaddbeginFL}{} %DIF PREAMBLE
\providecommand{\DIFaddendFL}{} %DIF PREAMBLE
\providecommand{\DIFdelbeginFL}{} %DIF PREAMBLE
\providecommand{\DIFdelendFL}{} %DIF PREAMBLE

\mdfdefinestyle{change}{%
  topline=false,
  leftline=true,
  rightline=false,
  bottomline=false
}

\newenvironment{change}[1][]{%
  \begin{mdframed}[frametitle={Changes starting in line #1:}, style=change]%
}{%
  \end{mdframed}%
}

\begin{document}
\maketitle

\setlength{\parindent}{0cm}

This document contains the responses to the comments of each reviewer followed
by the marked-up differences of the manuscript and the revised version. For each
comment the author's response and, if applicable, the corresponding changes in
the manuscript are listed. Line numbers of changes are given with respect to the
revised manuscript.

The two most prominent changes in the revised manuscript are:
\begin{itemize}
\item Addition of a figure showing the temporal delay between the active and
  passive observations, which we suppose explains the larger residuals for the
  C159 and C161 flight. Extension of the discussion of the residuals for those
  flights to mention the temporal offsets between the active and passive
  observations.
\item Addition of a figure  showing scatter plots of IWP and residuals of the
  $243\pm 2.5\ \unit{GHz}$ and $325\pm 9.5\ \unit{GHz}$ channels for flight B984,
  which hint at a weak relationship particle shape and residuals for this flight.
\end{itemize}

%
%\begin{itemize}
%\item We have switched to an airborne measurement set-up and
%   the manuscript has been modified accordingly.
%\item The text in the result section has been shortened.
%\item Redundant results for scene 2 have been placed in an appendix.
%\item The selection of tested retrieval habits has been revised and changed.
%\end{itemize}

We want to thank both reviewers for taking the time to read our manuscript and
provide valuable feedback. The feedback was very helpful in guiding our efforts
to improve the manuscript.

\section{Principal changes}

Many comments from both reviewers were related to the description of the
generation of the training data and the implementation of the retrievals. In
order to address these comments and avoid excessive growth of the main text of
the manuscript, we have added appendices that explain the generation of the
training data, the training itself and the application of the retrievals. We
have also rewritten much of Sec.~1 and 2 to improve the presentation of both the
scope of the manuscript and the design of the GPROF-NN retrievals.

In addition to that, an error in the simulated brightness temperatures for MHS
was discovered and corrected. We have updated the results for MHS.
While this improved the overall accuracy of the MHS retrievals, it did not affect the
study's main findings. Furthermore, we identified and corrected a minor issue in
our evaluation of GPROF that caused a slight overestimation of its accuracy.
Again, this correction did not affect the conclusions of the paper.


\chapter{Comments from reviewer 1}
\input{response_1_1}

\chapter{Comments from reviewer 2}
\input{response_1_2}

%\includepdf[pages=-]{amt_manuscript_diff}

\bibliographystyle{copernicus}
\bibliography{references}

\end{document}
